
\begin{tutorial}
  {}
  {tutorials-041}
  % {\daydateyear, \tutorialtimec \\\tutorialtimezone}
  {}
  {\TutLocB}
  {\TutLevelB}
\end{tutorial}


\tutorialabstract{}{}{}{}{tutorials-041}

\vspace{2ex}\centerline{\rule{.5\linewidth}{.5pt}}\vspace{2ex}
\setlength{\parskip}{1ex}\setlength{\parindent}{0ex}

%\begin{bio}
{\small
In alphabetical order,

{\bfseries Xin Luna Dong} is a Principal Scientist at Amazon, leading the efforts of constructing Amazon
Product Knowledge Graph. She was one of the
major contributors to the Google Knowledge Vault
project, and has led the Knowledge-based Trust
project, which is called the “Google Truth Machine”
by the Washington Post. She co-authored the book
“Big Data Integration”, was awarded ACM Distinguished Member, VLDB Early Career Research
Contribution Award for “advancing the state of the
art of knowledge fusion”, and Best Demo award
in Sigmod 2005. She serves on the VLDB endowment and PVLDB advisory committee, and was a PC co-chair for VLDB 2021, ICDE Industry 2019,
VLDB Tutorial 2019, Sigmod 2018 and WAIM
2015. She has given multiple tutorials on data
integration, graph mining, and knowledge management.

Email: {\tt lunadong@amazon.com} \\
Homepage: {\tt http://lunadong.com/} \\

{\bfseries Hannaneh Hajishirzi} is an Assistant Professor
at the Paul G. Allen School of Computer Science \& Engineering at the University of Washington.
She works on NLP, AI, and machine learning, particularly designing algorithms for semantic understanding, reasoning, question answering, and information extraction from multimodal data. She
has earned numerous awards for her research, including an Allen Distinguished Investigator Award,
a Google Faculty Research Award, a Bloomberg
Data Science Award, an Amazon Research Award,
and a SIGDIAL Best Paper Award.

Email: {\tt hannaneh@washington.edu} \\
Homepage: {\tt https://homes.cs.washington.edu/hannaneh/} \\

{\bfseries Colin Lockard} is a PhD student at the Paul G.
Allen School of Computer Science \& Engineering
at the University of Washington, where he has published papers on knowledge extraction from both
unstructured and semi-structured text.

Email: {\tt lockardc@cs.washington.edu}\\
Homepage: {\tt https://homes.cs.washington.edu/lockardc/} \\

{\bfseries Prashant Shiralkar} is an Applied Scientist in
the Product Graph team at Amazon. He currently works on knowledge extraction from semistructured data. Previously, he received a Ph.D.
from Indiana University Bloomington where his
dissertation work focused on devising computational approaches for fact checking by mining
knowledge graphs. His research interests include
machine learning, data mining, information extraction and NLP, and Semantic Web technologies.

Email: {\tt shiralp@amazon.com} \\
Homepage: {\tt https://sites.google.com/site/shiralkarprashant}

}
  
%\end{bio}