
\begin{tutorial}
  {}
  {tutorials-046}
  {\daydateyear, \tutorialtimea \ and \tutorialtimec \\\tutorialtimezone}
  {\TutLocE}
  {\TutLevelE}
\end{tutorial}


\tutorialabstract{}{}{}{}{tutorials-046}

\vspace{2ex}\centerline{\rule{.5\linewidth}{.5pt}}\vspace{2ex}
\setlength{\parskip}{1ex}\setlength{\parindent}{0ex}

{\small

{\bfseries Malihe Alikhani} is a 5th year Ph.D. student
in the department of Computer sSience at Rutgers University,
advised by Prof. Matthew Stone. She is pursuing a certificate in cognitive science through
the Rutgers Center for Cognitive Science and
holds a BA and MA in Mathematics. Her research aims at teaching machines to understand
and generate multimodal communication. She
is the recipient of the fellowship award for excellence in computation and data sciences from
Rutgers Discovery Informatics Institute in 2018
and the Anita Berg student fellowship in 2019.
Before joining Rutgers, she was a lecturer and
an adjunct professor of Mathematics and Statistics for a year at San Diego State University and
San Diego Mesa College. She has served as the
program committee of ACL, NAACL, EMNLP,
AAAI, ICRL, ICMI, and INLG and is currently
the associate editor of the Mental Note Journal.

email: {\tt ma1195@cs.rutgers.edu}\\
webpage: {\tt www.malihealikhani.com}

{\bfseries Matthew Stone} is professor and chair in the Department of Computer Science at Rutgers University; he holds a joint appointment in the Rutgers
Center for Cognitive Science. His research focuses on discourse, dialogue and natural language generation; he is particularly interested in leveraging semantics to make interactive systems easier to build and more human-like in their behavior. He was program co-chair for NAACL 2007,
general co-chair for SIGDIAL 2014. He has also
served as program co-chair for INLG and IWCS,
as an information officer for SIGSEM, and on
the editorial board for Computational Linguistics.

email: {\tt mdstone@cs.rutgers.edu} \\
website: {\tt www.cs.rutgers.edu/~mdstone/}

}