
\begin{tutorial}
  {}
  {tutorials-018}
  {\daydateyear, \tutorialtimeb \\\tutorialtimezone}
  {\TutLocC}
  {\TutLevelC}
\end{tutorial}


\tutorialabstract{}{}{}{}{tutorials-018}

\vspace{2ex}\centerline{\rule{.5\linewidth}{.5pt}}\vspace{2ex}
\setlength{\parskip}{1ex}\setlength{\parindent}{0ex}

%\begin{bio}
{\small
In alphabetical order,

{\bfseries Kevin Bretonnel Cohen} has written, overseen,
and received hundreds of reviews in his capacity as deputy editor-in-chief of a biomedical informatics journal, associate editor of five natural language processing or bioinformatics journals, special issue editor, workshop organizer, and author
of 100+ publications in computational linguistics
and natural language processing. His forthcoming
book Writing about data science research: With
examples from machine and natural language processing includes coverage of a number of aspects
of the reviewing process. His current research focuses on issues of reproducibility.

{\bfseries Karën Fort} is an associate professor at Sorbonne
Universite. Besides being a reviewer for most major NLP conferences, she has been editor in chief
for a Traitement automatique des langues journal
special issue on ethics and acted as Area Chair
for ACL in 2017 and 2018 (as senior AC). Her
main research interests are ethics, and the construction of language resources for natural language processing. She co-authored the report on
the EMNLP reviewer survey (Névéol et al., 2017).

{\bfseries Margot Mieskes} is a professor at the Darmstadt
University of Applied Sciences and as such has a
lot experience teaching, also in culturally diverse
settings, which are prevalent in German Universities of Applied Sciences. Additionally, she has written and received a number of reviews in conferences as well as journals. She is a member of
the ACL Professional Conduct Committee and an
active member of the Widening NLP efforts. Her
research interests are in summarization and summarization evaluation, replicability, repeatability
and transparency of NLP experiments in general.

{\bfseries Aurélie Névéol} is a permanent researcher at
LIMSI CNRS and Universite Paris Saclay. She ´
has been involved in reviewing natural language
processing papers at many stages of the reviewing process, including: reviewer, associate editor for three journals, area chair for *ACL and
bioinformatics conferences, workshop organizer.
Her research focuses on biomedical natural language processing as well as ethics issues in NLP
research. She co-authored the report on EMNLP
reviewer survey (Névéol et al., 2017).

}
  
%\end{bio}