\section{Session 9: Best Paper Session (Sponsored by Apple \& Amazon)}
\setheaders{Session 9}{\daydateyear}

\begin{center}
  {\Large \bf The process for selecting best papers and honourable mentions}
\end{center}

\vspace*{0.5cm}

The Program Committee Co-Chairs (PCs) have defined a multi-step process. Area Chairs (ACs) were asked to select a number of top papers in their areas satisfying as many as possible of the following criteria:
\begin{itemize}
\item high quality
\item nominated for the award by at least one primary reviewer
\item bringing disruptive ground-breaking innovation as compared to the current mainstream
\end{itemize}

ACs re-read their finalists and discussed among themselves the merits of the nominee's work with the help of the primary reviews. ACs then submitted the papers to the PCs along with their selection decisions. PCs balanced ACs' nominations for diversity and representativeness among areas and the review consistency. They  prepared the papers in Softconf for best-paper reviewing and selection. There were 52 best paper candidates.

In parallel, PCs formed the best paper selection committee (BPC) from 22 experts in the field with a mix of expertise and backgrounds and at a good seniority level. In case of COIs, the BPC member was excluded from the further evaluation process. BPC members reviewed 6-8 papers each and provided a short review with respect to the best paper criteria.

Based on BPC recommendations, there were about 20 papers left in the pool. PCs then re-read those papers and discussed their particular merits. Finally, 6 long papers and 2 short papers were selected as honourable mentions. For the best papers, 3 long papers and 2 short papers were selected for presentation in the closing conference session.

The selected honourable mentions and best papers emphasize the diversity of the ACL in terms of research questions, methods, and interdisciplinarity.

\paragraph{Best Long Papers}

\begin{itemize}
\item \textit{Finding syntax in human encephalography with beam search.} John Hale, Chris Dyer, Adhiguna Kuncoro and Jonathan Brennan.
\item \textit{Learning to Ask Good Questions: Ranking Clarification Questions using Neural Expected Value of Perfect Information.} Sudha Rao and Hal Daumé III.
\item \textit{Let’s do it “again”: A First Computational Approach to Detecting Adverbial Presupposition Triggers.} Andre Cianflone, Yulan Feng, Jad Kabbara and Jackie Chi Kit Cheung.
\end{itemize}

\paragraph{Best Short Papers}

\begin{itemize}
\item \textit{Know What You Don’t Know: Unanswerable Questions for SQuAD.} Pranav Rajpurkar, Robin Jia and Percy Liang.
\item \textit{‘Lighter’ Can Still Be Dark: Modeling Comparative Color Descriptions.} Olivia Winn and Smaranda Muresan.
\end{itemize}
