\begin{tutorial}
  {Beyond Multiword Expressions: Processing Idioms and Metaphors}
  {tutorial-025}
  {\daydateyear, \tutorialafternoontime}
  {\TutLocE}
\end{tutorial}

Idioms and metaphors are characteristic to all areas of human activity and to
all types of discourse. Their processing is a rapidly growing area in NLP,
since they have become a big challenge for NLP systems. Their omnipresence in
language has been established in a number of corpus studies and the role they
play in human reasoning has also been confirmed in psychological experiments.
This makes idioms and metaphors an important research area for computational
and cognitive linguistics, and their automatic identification and
interpretation indispensable for any semantics-oriented NLP application.

This tutorial aims to provide attendees with a clear notion of the linguistic
characteristics of idioms and metaphors, computational models of idioms and
metaphors using state-of-the-art NLP techniques, their relevance for the
intersection of deep learning and natural language processing, what methods and
resources are available to support their use, and what more could be done in
the future. Our target audience are researchers and practitioners in machine
learning, parsing (syntactic and semantic) and language technology, not
necessarily experts in idioms and metaphors, who are interested in tasks that
involve or could benefit from considering idioms and metaphors as a pervasive
phenomenon in human language and communication.


\vspace{2ex}\centerline{\rule{.5\linewidth}{.5pt}}\vspace{2ex}
\setlength{\parskip}{1ex}\setlength{\parindent}{0ex}



  {\bfseries Valia Kordoni} is a professor at Humboldt University
Berlin (Deputy Chair for the subject area “English
Linguistics”). She is a leader in EU-funded
research in Machine Translation, Computational
Semantics, and Machine Learning. She has organized
conferences and workshops dedicated to
research on MWEs, recently including the EACL
2014 10th Workshop on Multiword Expressions
(MWE 2014) in Gothenburg, Sweden, the NAACL
2015 11th Workshop on Multiword Expressions in
Denver, Colorado, and the ACL 2016 12th Workshop
on Multiword Expressions in Berlin, Germany,
among others. She has been the Local Chair
of ACL 2016 - The 54th Annual Meeting of the
Association for Computational Linguistics which
took place at the Humboldt University Berlin in
August 2016. Recent activities of hers include a
tutorial on Robust Automated Natural Language
Processing with Multiword Expressions and Collocations
in ACL 2013, as well as a tutorial on
Beyond Words: Deep Learning for Multiword Expressions
and Collocations in ACL 2017. She is
the author of Multiword Expressions - From Linguistic
Analysis to Language Technology Applications
(to appear, Springer).

