\section{Message from the General Chair}\vspace{2em}
\setheaders%
    {Message from the General Chair}%
    {Message from the General Chair}
\thispagestyle{emptyheader}

\setlength{\parskip}{.7ex}

It is my delightful duty as General Chair to sit at 
my kitchen table here in San Francisco and write these words welcoming you to the 58th
Annual Meeting of the Association for Computational Linguistics.

Our conference this year is of course very different than in the past;
I'll be attending the conference from my kitchen table as well.
This is our first experience of ACL as a virtual conference, a 
shift due to a great trial to all of us, the COVID-19 virus.

Our hope in designing this year's conference was to draw strength from this tragedy and come together
as a community. We wanted the conference to offer a beacon of inclusion,
making it much easier for people all over the globe, whatever
their resources or backgrounds, to come to share their knowledge
and learn from each other, in a safe, welcoming, and exciting environment.
And we wanted the conference to offer a message of sustainability,
proving that even without the environmental costs of thousands of people flying around the globe,
and despite the lack of face-to-face cameraderie that helps bind us together,
we could nonetheless send our words and thoughts and
around the globe and build something together in another way.

Our challenge was to do so in a few months, and with little prior experience of our own.
I am so proud of our program chairs Joyce Chai, Natalie Schluter, and Joel Tetreault,
and the entire organizing committee, for rising to the challenge and putting together this wonderful meeting.

We have many people to thank.  Joyce, Natalie, and Joel, as is our ACL custom,
bore the brunt of the organizational burden, and managed beautifully despite all the
simultaneous demands of the whirlwinds of their daily
work and home lives.  The unflappable and wise Priscilla Rasmussen.
The amazing 52-person organizing committee, who all turned on a dime
to make the conference work virtually: Local Chairs (Jianfeng Gao, Luke Zettlemoyer), Tutorial Chairs (Agata Savary, Yue Zhang),
Workshop Chairs (Milica Ga\v{s}i\'{c}, Dilek Hakkani-Tur, Saif M. Mohammad, Ves Stoyanov),
Student Research Workshop Chairs (Rotem Dror, Jiangming Liu, Shruti Rijhwani, Yizhong Wang),
Faculty Advisors to the Student Research Workshop (Omri Abend, Sujian Li, Zhou Yu),
Conference Handbook Chair (Nanyun Peng),
Demonstration Chairs (Asli Celikyilmaz, Shawn Wen),
Diversity and Inclusion Chairs (Cecilia Ovesdotter Alm, Vinodkumar Prabhakaran),
Diversity and Inclusion Sub-Committee Chairs (Academic Inclusion Chairs: Aakanksha Naik, Emily Prud'hommeaux, Alla Rozovskaya;
Accessibility Chairs: Sushant Kafle, Masoud Rouhizadeh, Naomi Saphra;
Childcare Chairs: Khyathi Chandu, Stephen Mayhew;
Financial Access Chairs: Allyson Ettinger, Ryan Georgi, Tirthankar Ghosal;
Socio-cultural Inclusion Chairs: Shruti Palaskar, Maarten Sap),
Local Sponsorship Chairs (Hoifung Poon, Kristina Toutanova),
Publication Chairs (Steven Bethard, Ryan Cotterell, Rui Yan),
Virtual Infrastructure Chairs (Hao Fang, Sudha Rao),
Virtual Infrastructure Committee (Yi Luan, Hamid Palangi, Lianhui Qin, Yizhe Zhang),
Publicity Chairs (Emily M. Bender, Esther Seyffarth),
Sustainability Chairs (Ananya Ganesh, Klaus Zechner),
Student Volunteer Coordinator (Marjan Ghazvininejad),
Website Chairs (Sudha Rao, Yizhe Zhang)

The ACL Executive Committee gave excellent guidance and advice. Extra-special thanks to
ACL Officers Nitin Madnani, Matt Post,  and David Yarowsky.
We drew heavily on the infrastructure pioneered by Sasha Rush and
the ICLR organization committee at ICLR 2020, together with lots
of advice from the organizers of other virtual conferences and the
ACM.

We are, as always, extremely grateful to our sponsors, listed on the previous page.

And finally, thanks to you, the thousands of members of our community
who made this conference possible by writing papers, recording talks, reviewing and area chairing the papers,
being invited speakers, and perhaps most important, by reading

\bigskip
\noindent Dan Jurafsky \index{Jurafsky, Dan}\\
\noindent ACL 2020 General Chair\\
\noindent July 2020\\